Impacts of Social Backgrounds on People's Perception of the Risk of Getting AIDS

### 2022-04-11 outputs/paper/Kenya_DHS_1998.Rmd
update to paper

(Figure \@ref(fig:comarm)) showcases the correlation between participants’ marital status past 12 months and participants' selected survey answers through both linear and non-linear lines. For female and male participants, the line depicts that the “no risk at all” to the chances of getting AID increases once the participant is not married or is formerly married. Overall, the perception of getting AIDS amongst male and female participants is positively correlated to the marital status, in terms of it increases when they’re currently married, to never married as expected. The relationship between the perception of getting AIDS and it being a “small”, “moderate” and “great” risk almost show a similar pattern for male and female participants both. Their perception of AIDS being a “small” risk is lower for those currently married, increases once formerly married, and decreases when never married, this pattern is similar to the male participants' “great” and “moderate” perception of getting AIDS as well.  The pattern for “great” and “moderate” chances for female participants has a similar linear trend as they’re decreasing.

The difference between the perception of male and female participants as shown in the graph (Figure \@ref(fig:maritalm)) and (Figure \@ref(fig:maritalf)) are based on several factors, some of which may include differences in societal expectations for men versus women, education, customs, and ideologies.

@@

(Figure \@ref(fig:coress)) showcases the correlation between participants’ region of residence and participants' selected survey answers through both linear and non-linear lines. From societal understanding, it would be safe to assume that residents living in the urban area would have more access to information and the safety of diseases as there would be more sources of accessing that information. Thus, it is reasonable to assume that residents who reside in urban areas would have more behavioral changes in terms of perception of the chances of getting AIDS, due to the comparitve influx of information. Thus, we should expect downwards trends for both survey answers “no risk at all”, “moderate” and “small” for urban compared to rural. Overall, the figure for female participants showcased a similar trend as expected.

@@

**Collection Process**
1. How was the data associated with each instance acquired?
  - The data set was collected by the DHS program in Kenya. Details can be found in the Data Methodology section of the report.
2. What mechanisms or procedures were used to collect the data (e.g., hardware apparatuses or sensors, manual human curation, software programs, software APIs)?
- Household questionnaires, in-person interviews, and other types of model questionnaires were employed. 
3. If the dataset is a sample from a larger set, what was the sampling strategy (e.g., deterministic, probabilistic with specific sampling probabilities)?
- The enumeration areas are drawn from census files, and samples of households were selected from the enumeration areas.
4. Who was involved in the data collection process (e.g., students, crowdworkers, contractors) and how were they compensated (e.g., how much were crowdworkers paid)?
- The DHS program members were involved in the data collection process.
5. Over what timeframe was the data collected?
- The data used in this report was collected in 1998.
6. Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (e.g., websites)?
- The data is obtained from the official website of the DHS program. The link is https://dhsprogram.com/
7. Were the individuals in question notified about the data collection?
- The individuals of the question are well aware of the survey as well as the data collection.
8. Did the individuals in question consent to the collection and use of their data?
- The individuals in question have consented to the collection and use of their data.
9. If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses?
- There’s no open information available to tell if the consent for revokes were granted to the survey participants.
10. Has an analysis of the potential impact of the dataset and its use on data subjects (e.g., a data protection impact analysis) been conducted?
- The analysis of the original survey data was conducted by the National Council for Population and 11. Development of the Republic of Kenya. The link to the report is: https://dhsprogram.com/pubs/pdf/FR102/FR102.pdf
12. Any other comments?
- None.

@@

**Uses**
1. Has the dataset been used for any tasks already?
- The dataset has not been used for other tasks yet.
2. Is there a repository that links to any or all papers or systems that use the dataset?
- https://github.com/R300G/Kenya_Demographic_1998.git
3. What (other) tasks could the dataset be used for?
- The dataset would be used for understanding behavior to disease amongst different socio-economic demographic
4. Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses?
- The cleaning process is very specific to the way this table was formatted in the original PDF and may not work on other tables.

>>>>

Figure \@ref(fig:comarm) showcases the correlation between participants’ marital status past 12 months and participants' selected survey answers through both linear and non-linear lines. For female and male participants, the line depicts that the “no risk at all” to the chances of getting AID increases once the participant is not married or is formerly married. Overall, the perception of getting AIDS amongst male and female participants is positively correlated to the marital status, in terms of it increases when they’re currently married, to never married as expected. The relationship between the perception of getting AIDS and it being a “small”, “moderate” and “great” risk almost show a similar pattern for male and female participants both. Their perception of AIDS being a “small” risk is lower for those currently married, increases once formerly married, and decreases when never married, this pattern is similar to the male participants' “great” and “moderate” perception of getting AIDS as well.  The pattern for “great” and “moderate” chances for female participants has a similar linear trend as they’re decreasing.

The difference between the perception of male and female participants as shown in the graph Figure \@ref(fig:maritalm) and Figure \@ref(fig:maritalf) are based on several factors, some of which may include differences in societal expectations for men versus women, education, customs, and ideologies.

@@

Figure \@ref(fig:coress) showcases the correlation between participants’ region of residence and participants' selected survey answers through both linear and non-linear lines. From societal understanding, it would be safe to assume that residents living in the urban area would have more access to information and the safety of diseases as there would be more sources of accessing that information. Thus, it is reasonable to assume that residents who reside in urban areas would have more behavioral changes in terms of perception of the chances of getting AIDS, due to the comparitve influx of information. Thus, we should expect downwards trends for both survey answers “no risk at all”, “moderate” and “small” for urban compared to rural. Overall, the figure for female participants showcased a similar trend as expected.

@@

**Collection Process**

1. How was the data associated with each instance acquired?
  - The data set was collected by the DHS program in Kenya. Details can be found in the Data Methodology section of the report.
2. What mechanisms or procedures were used to collect the data (e.g., hardware apparatuses or sensors, manual human curation, software programs, software APIs)?
- Household questionnaires, in-person interviews, and other types of model questionnaires were employed. 
3. If the dataset is a sample from a larger set, what was the sampling strategy (e.g., deterministic, probabilistic with specific sampling probabilities)?
- The enumeration areas are drawn from census files, and samples of households were selected from the enumeration areas.
4. Who was involved in the data collection process (e.g., students, crowdworkers, contractors) and how were they compensated (e.g., how much were crowdworkers paid)?
- The DHS program members were involved in the data collection process.
5. Over what timeframe was the data collected?
- The data used in this report was collected in 1998.
6. Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (e.g., websites)?
- The data is obtained from the official website of the DHS program. The link is https://dhsprogram.com/
7. Were the individuals in question notified about the data collection?
- The individuals of the question are well aware of the survey as well as the data collection.
8. Did the individuals in question consent to the collection and use of their data?
- The individuals in question have consented to the collection and use of their data.
9. If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses?
- There’s no open information available to tell if the consent for revokes were granted to the survey participants.
10. Has an analysis of the potential impact of the dataset and its use on data subjects (e.g., a data protection impact analysis) been conducted?
- The analysis of the original survey data was conducted by the National Council for Population and 11. Development of the Republic of Kenya. The link to the report is: https://dhsprogram.com/pubs/pdf/FR102/FR102.pdf
12. Any other comments?
- None.

@@

**Uses**

1. Has the dataset been used for any tasks already?
- The dataset has not been used for other tasks yet.
2. Is there a repository that links to any or all papers or systems that use the dataset?
- https://github.com/R300G/Kenya_Demographic_1998.git
3. What (other) tasks could the dataset be used for?
- The dataset would be used for understanding behavior to disease amongst different socio-economic demographic
4. Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses?
- The cleaning process is very specific to the way this table was formatted in the original PDF and may not work on other tables.
